---
title: "The Title of Your Document"
author: "Your Name"
date: "`r format(Sys.time(), '%d&period; %B %Y')`"
output: 
    word_document:
      reference_docx:  C:\Users\Malcolm\Dropbox\A_Book\book\trialreferencestyle.docx
      toc: true
      toc_depth: 3
      fig_caption: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE)

options(knitr.kable.NA = "",
        knitr.table.format = "pandoc")

wkdir <- "./../../A_Book/book/"

options("show.signif.stars"=FALSE,"stringsAsFactors"=FALSE,
        "max.print"=50000,"width"=240)

#library(X)
library(knitr)
library(captioner)
# library(Y)
# library(Z)

tab_nums <- captioner(prefix = "Table")
fig_nums <- captioner(prefix = "Figure")
equ_nums <- captioner(prefix = "Equ.")


```

# Introduction



```{r}
ans <- matrix(rnorm(25),ncol=5,nrow=5,dimnames=list(1:5,1:5))

```

`r tab_nums("t1", caption=" 25 random normal numbers illustrating the use of tab_nums.")`

```{r echo=FALSE}
kable(ans,digits=c(3,3,3,3,3),row.names = TRUE)

```



And here is a bunch of informative text.


# Methods



```{r fig.width=4.75, fig.height=2.75, echo=FALSE}
data(faithful)
par(mfrow=c(1,1),mai=c(0.45,0.45,0.05,0.05),oma=c(0,0,0,0)) 
par(cex=0.75, mgp=c(1.35,0.35,0), font.axis=7,font=7,font.lab=7) 
hist(faithful[,"eruptions"],breaks=24,col=2,main="")
label <- " A quick example using the faithful eruption data to illustrate the use of fig_nums."
```

`r fig_nums("f1",caption=label)`


Yet nore text introducing the following equation.

The concept of confidence intervals (often 90% or 95% CI) is classically defined in Snedecor and Cochran (1967, 1989), and very many others, as:

`r equ_nums("e1")`

$$\bar{x}\pm {{t}_{\nu}}\frac{\sigma }{\sqrt{n}}$$

where $\hat{x}$ is the mean of the sample of $n$ observations, and we refer to __Equ `r equ_nums("e1", display="num")`__.  Notice that I did not use a fullstop when refering to equation 1. Try running the macro with and without a fullstop to see why.

Of course you will need to provide your own reference document and modify the styles within that to get the formatting you desire.









<!-- ```{r child="i_References.Rmd"} -->

<!-- ``` -->
